%
% Project name   :
% File name      : abstract.tex
% Created date   : Mon 17 Jul 2017 10:29:12 AM +07
% Author         : Ngoc-Sinh Nguyen
% Last modified  : Sat 29 Jul 2017 03:33:28 PM ICT
% Desc           :
%
\begin{abstract}
Histogram of Oriented Gradient (HOG) is a popular feature description for the purpose of object detection.
However, HOG algorithm requires a performance system because of its complex
operation set.
Especially, the cell histogram generation is one
of the most complex part, it uses inverse tangent, square, square root, floating
point multiplication.
In this paper, we propose an \MakeLowercase{\@title}.
%\del{,which is suitable for low resource system and hardware implementation}.
%\del{It determines the quantized angles exactly from bounding the \textit{tan}
%values of quantized angles by rational numbers from ratio between the pixel
%derivatives with respect to both  \textit{y} and \textit{x} direction}.
It employs the bin's boundary angle method to determine the two quantized angles.
However, instead of choosing an approximate value of tan, the nearest
greater and the nearest  smaller of each \textit{tan} values from ratio between
pixel's derivative in $y$ and $x$ direction are used.
Magnitude of two bins are  solutions of a system of two equations, which
represent the equality of the gradient of a pixel and  its two
bins in both vertical and horizontal direction.
The proposed method spends only 30 addition and 40 shift operations to identify
two bins of a pixel.
Simulation results show that the percentage error when reconstructing the
difference in $x$ and $y$ direction are  always less than 2\% with 8-bit length of the fractional part.
Additionally, manipulating the precision of gradient  magnitude
is very simple by pre-defined \textit{sine} and \textit{cosine}  values of quantized angles.
Synthesizing the hardware implementation presents that its area cost is 3.57\textit{KGates} with
45\textit{nm} NanGate standard cell library.
The hardware module runs at the maximum frequency of 400 MHz, and the throughput is
0.4 (\textit{pixel/ns}) for a single module.
It is able to support about 48\textit{fps} with $4K$ UHD resolution.


\end{abstract}


